\documentclass[
  english,
  a4paper,
  pagemark,
  stamp]{sdaps}
\usepackage[utf8]{inputenc}
\usepackage{multicol}

\author{Pierre-Évariste Dagand}
\title{MPRI 2.4 -- Dependently-Typed Programming}

\begin{document}
  % Everything you do should be done inside the questionnaire environment.

  % If you don't like the default text at the beginning of each questionnaire
  % you can remove it with the optional [noinfo] parameter for the environment 
  \begin{questionnaire}
    % There is a predefined "info" style to hilight some text.
    \begin{info}
      By ``the course'', I mean the last part of MPRI 2.4, on the topic of ``dependently-typed functional programming''.
    \end{info}

    % Use \addinfo to add metadata (which is printed on the report later on)
    \addinfo{Date}{23/02/2018}

    \section{Overall impressions}

    \singlemark{The lectures explain clearly the various topics.}
               {strongly disagree}{strongly agree}
    \singlemark{The support material (Agda code, PDF) is complete.}
               {strongly disagree}{strongly agree}
    \singlemark{The amount of personal investment (e.g., homework) required is reasonable.}
               {strongly disagree}{strongly agree}
    \singlemark{My personal investment matched the requirements of this course.}
               {strongly disagree}{strongly agree}
    \singlemark{The exercises are interesting and complement the lectures.}
               {strongly disagree}{strongly agree}
    \singlemark{My previous knowledge was sufficient to follow the course.}
               {strongly disagree}{strongly agree}
    \singlemark{This course made me a better programmer.}
               {strongly disagree}{strongly agree}
    \singlemark{How do you judge the professor pedagogical skills and investment in this course?}
               {poor}{great}
    \singlemark{How interesting did you find the topics (effects, indexing, recursion, genericity) treated during this course?}
               {absolutely uninteresting}{very interesting}
    \singlemark{How satisfied are you with this course?}
               {very disappointed}{very satisfied}
    \singlemark{How you would qualify the overlap with other MPRI courses (eg., MPRI 2.7.2)?}
               {no overlap}{absolutely redundant}


    \section{Improvements}

    \singlemark{How would you qualify the amount of live coding performed in class?}
               {not enough}{too much}
    \singlemark{How would you qualify the speed at which the explanations were given in class?}
               {too slow}{too fast}
    \singlemark{How would you qualify the difficulty of this course?}
               {too easy}{too difficult}
    \singlemark{How would you qualify the amount of exercises in the lecture notes?}
               {not enough}{too much}
    \singlemark{How would you qualify the amount of meta-theory introduced in this course?}
               {insufficient}
               {excessive}
    \singlemark{How would you qualify the amount of mathematical proofs presented in class?}
               {insufficient}{excessive}
    \singlemark{How would you quantify the background in dependent type theory necessary to follow this course?}
               {absolutely unnecessary}{absolutely necessary}
    \singlemark{In a typical lecture, would you have preferred:}
               {less material/more thorough treatment}
               {more material \& superficial treatment}

    \section{Open Mic}

    \textbox{1.5cm}{Did you have any particular difficulty during this class?}

    \textbox{1.5cm}{Any comments/suggestions? }
    \def\checkboxstyle{box}

  \end{questionnaire}
\end{document}

